Supplementary Material (SM)

### 2020-04-28 Current-Version.Rmd
organize for overleaf

ggsave("~/Gits/branching.brownian.motion.and.spde/Current Version/wn.png",wn,width=5,height=2.5)
```

@@

ggsave("~/Gits/branching.brownian.motion.and.spde/Current Version/rescaled_plots.png",rescaled_plots,device="png",width=6,height=6,units="in",dpi=350)
```

@@

ggsave("~/Gits/branching.brownian.motion.and.spde/Current Version/community_dynamics.png",community_plot,width=6.5,height=5,dpi=320)

@@

ggsave("~/Gits/branching.brownian.motion.and.spde/Current Version/on_pl.png",on_pl,device="png",width=3.5,height=3.5,units="in",dpi=350)

@@

ggsave("~/Gits/branching.brownian.motion.and.spde/Current Version/interaction_networks.png",coevs,device="png",width=6,height=6,units="in",dpi=350)

@@

ggsave("~/Gits/branching.brownian.motion.and.spde/Current Version/on_pl.png",on_pl2,device="png",width=3.5,height=3.5,units="in")
```

@@

\begin{subequations}\label{cov_eqns}
\begin{multline}\label{cov_alpha_beta}
\mathrm{Cov}_{f_{\bar X}}(\alpha,|\beta|)=\frac{2c^2b^2U^4N}{\pi\bar r}\sqrt\frac{V_{\bar X}}{2\pi} \\
\times\left(\frac{1}{(1+8bV_{\bar X})^{3/4}}-\frac{1}{(1+4bV_{\bar X})^{3/4}(1+2bV_{\bar X})^{1/2}}\right),
\end{multline}
\begin{equation}\label{cov_alpha_gamma}
\mathrm{Cov}_{f_{\bar X}}(\alpha,\gamma)=\frac{c^2b^2U^4N}{2\pi\bar r}(1-2bV_{\bar X})\left(\frac{1}{\sqrt{1+4bV_{\bar X}}}-\frac{1}{1+2bV_{\bar X}}\right).
\end{equation}
\end{subequations}
```{r, eval=F, echo=F}
c=1e-4
b=1e-1
r=0.1
N=1e10
Cov_ab <- function(x){
  # x <- 2*b*V_{\bar X}
  val = 2*c^2*b^2*N / (pi*r)
  val = val * sqrt(x/(2*b*pi))
  val2 = (1+8*x/2)^(-0.75)
  val3 = (1+4*x/2)^(-0.75) / sqrt(1+2*x/2)
  val = val * (val2 - val3)
  return(val)  
}
Cov_ag <- function(x){
  # x <- 2*b*V_{\bar X}
  val = 2*c^2*b^2*N / (2*pi*r)
  val = val * (1-2*x/2)
  val2 = 1 / sqrt(1+4*x/2)
  val3 = 1 / (1+2*x/2)
  val = val * (val2 - val3)
  return(val)  
}
require(ggplot2)
require(ggthemes)
require(gridExtra)
dummy <- ggplot(data = data.frame(x = 0), mapping = aes(x = x))
cov_ab_p <- dummy + stat_function(fun = Cov_ab) + ylim(-0.4,0.4) + xlim(0,2) + theme_minimal() + xlab("Approximate ratio of variance among \n species to variance within species") + ylab("Covariance of \u03B1 and |\u03B2|")
cov_ag_p <- dummy + stat_function(fun = Cov_ag) + ylim(-0.4,0.4) + xlim(0,2) + theme_minimal() + xlab("Approximate ratio of variance among \n species to variance within species") + ylab("Covariance of \u03B1 and \u03B3")
cov_plot <- grid.arrange(cov_ab_p,cov_ag_p,nrow=1) 
ggsave("~/Gits/branching.brownian.motion.and.spde/Current Version/cov.png",cov_plot,width=6.5,height=2.5)
```

```{r, echo=F, fig.align='center', out.width='100%', fig.cap='\\label{cov_fig}Curves representing the covariance between the magnitude of linear selection gradients and competition coefficients (left) and between stabilizing selection gradients and competition coefficients (right) as a function of $2bV_{\\bar X}$ which is approximately equal to the ratio of variance in mean traits among species to the intraspecific trait variance. In both plots we set $c=1.0\\times10^{-4}$, $b=0.1$, $\\bar r=0.1$ and $N=1.0\\times10^{10}$ and let $V_{\\bar X}$ vary.'}
knitr::include_graphics('/home/bb/Gits/branching.brownian.motion.and.spde/Current Version/cov.png')
```
We visualize these relationships in Figure \ref{cov_fig} for fixed $c,b,\bar r,U$ and $N$. In SM \S\ref{coef_grad_moms} we verify the qualitative nature of these relationships by repeating numerical integrations of system (\ref{comm_dynamics}) across a set of randomly drawn model parameters. We designed our numerical approach to inherit the assumptions of symmetric model parameters such as mutation rates $\mu_1=\dots=\mu_S$ and abiotic optima $\theta_1=\dots=\theta_S$ and to relax the key assumptions of normally distributed mean traits along with constant additive genetic variances and abundances across species.

@@

```{r, eval=F, echo=F}
require(ggplot2)
require(gridExtra)
df = read.csv("~/Research/Branching Brownian Motion/corrs.csv")
Cαβp = ggplot(df,aes(x=df$V/df$σ,y=df$Cαβ))+geom_point(size=0.1)+stat_smooth(color="black", method = "lm", formula = y ~ x + I(x^2) + I(x^3))+theme_minimal() + ylab("Correlation of \u03B1 and \u03B2")+xlab("Ratio of variance among \n species to variance within species")
Cαabsβp = ggplot(df,aes(x=df$V/df$σ,y=df$Cαabsβ))+geom_point(size=0.1)+stat_smooth(color="black", method = "lm", formula = y ~ x + I(x^2) + I(x^3))+theme_minimal()+ylab("Correlation of \u03B1 and |\u03B2|")+xlab("Ratio of variance among \n species to variance within species")
Cαγp = ggplot(df,aes(x=df$V/df$σ,y=df$Cαγ))+geom_point(size=0.1)+stat_smooth(color="black", method = "lm", formula = y ~ x + I(x^2) + I(x^3))+theme_minimal()+ylab("Correlation of \u03B1 and \u03B3")+xlab("Ratio of variance among \n species to variance within species")
Cαℭp = ggplot(df,aes(x=df$V/df$σ,y=df$Cαℭ))+geom_point(size=0.1)+stat_smooth(color="black", method = "lm", formula = y ~ x + I(x^2) + I(x^3))+theme_minimal()+ylab("Correlation of \u03B1 and ℭ")+xlab("Ratio of variance among \n species to variance within species")
corrsp = grid.arrange(Cαabsβp,Cαγp,nrow=1)
ggsave("/home/bb/Gits/branching.brownian.motion.and.spde/Current Version/corrs.png",  corrsp,  width=6.5,height=2.5)
ggsave("/home/bb/Gits/branching.brownian.motion.and.spde/Current Version/Cαℭp.png",   Cαℭp,  width=4,height=2.5)
```

```{r, echo=F, fig.align='center', out.width='60%', fig.cap='\\label{cor_coev_fig}Numerical estimates for the correlation of the strength of coevolution measured by $\\mathfrak{C}$ and competition coefficeints $\\alpha$ plotted against the variance of mean traits among species divided by the mean variance of traits within species. Each dot represents the result from a single simulation. The red line is a cubic regression.'}
knitr::include_graphics('/home/bb/Gits/branching.brownian.motion.and.spde/Current Version/Cαℭp.png')
```

>>>>

ggsave("~/Gits/branching.brownian.motion.and.spde/wn.png",wn,width=5,height=2.5)
```

@@

ggsave("~/Gits/branching.brownian.motion.and.spde/rescaled_plots.png",rescaled_plots,device="png",width=6,height=6,units="in",dpi=350)
```

@@

ggsave("~/Gits/branching.brownian.motion.and.spde/community_dynamics.png",community_plot,width=6.5,height=5,dpi=320)

@@

ggsave("~/Gits/branching.brownian.motion.and.spde/on_pl.png",on_pl,device="png",width=3.5,height=3.5,units="in",dpi=350)

@@

ggsave("~/Gits/branching.brownian.motion.and.spde/interaction_networks.png",coevs,device="png",width=6,height=6,units="in",dpi=350)

@@

ggsave("~/Gits/branching.brownian.motion.and.spde/on_pl.png",on_pl2,device="png",width=3.5,height=3.5,units="in")
```

@@

\begin{subequations}\label{cov_eqns}
\begin{multline}\label{cov_alpha_beta}
\mathrm{Cov}_{f_{\bar X}}(\alpha,|\beta|)=\frac{2c^2b^2U^4N}{\pi\bar r}\sqrt\frac{V_{\bar X}}{2\pi} \\
\times\left(\frac{1}{(1+8bV_{\bar X})^{3/4}}-\frac{1}{(1+4bV_{\bar X})^{3/4}(1+2bV_{\bar X})^{1/2}}\right),
\end{multline}
\begin{equation}\label{cov_alpha_gamma}
\mathrm{Cov}_{f_{\bar X}}(\alpha,\gamma)=\frac{c^2b^2U^4N}{2\pi\bar r}(1-2bV_{\bar X})\left(\frac{1}{\sqrt{1+4bV_{\bar X}}}-\frac{1}{1+2bV_{\bar X}}\right).
\end{equation}
\end{subequations}
```{r, eval=F, echo=F}
c=1e-4
b=1e-1
r=0.1
N=1e10
Cov_ab <- function(x){
  # x <- 2*b*V_{\bar X}
  val = 2*c^2*b^2*N / (pi*r)
  val = val * sqrt(x/(2*b*pi))
  val2 = (1+8*x/2)^(-0.75)
  val3 = (1+4*x/2)^(-0.75) / sqrt(1+2*x/2)
  val = val * (val2 - val3)
  return(val)  
}
Cov_ag <- function(x){
  # x <- 2*b*V_{\bar X}
  val = 2*c^2*b^2*N / (2*pi*r)
  val = val * (1-2*x/2)
  val2 = 1 / sqrt(1+4*x/2)
  val3 = 1 / (1+2*x/2)
  val = val * (val2 - val3)
  return(val)  
}
require(ggplot2)
require(ggthemes)
require(gridExtra)
dummy <- ggplot(data = data.frame(x = 0), mapping = aes(x = x))
cov_ab_p <- dummy + stat_function(fun = Cov_ab) + ylim(-0.4,0.4) + xlim(0,2) + theme_minimal() + xlab("Approximate ratio of variance among \n species to variance within species") + ylab("Covariance of \u03B1 and |\u03B2|")
cov_ag_p <- dummy + stat_function(fun = Cov_ag) + ylim(-0.4,0.4) + xlim(0,2) + theme_minimal() + xlab("Approximate ratio of variance among \n species to variance within species") + ylab("Covariance of \u03B1 and \u03B3")
cov_plot <- grid.arrange(cov_ab_p,cov_ag_p,nrow=1) 
ggsave("~/Gits/branching.brownian.motion.and.spde/cov.png",cov_plot,width=6.5,height=2.5)
```

```{r, echo=F, fig.align='center', out.width='100%', fig.cap='\\label{cov_fig}Curves representing the covariance between the magnitude of linear selection gradients and competition coefficients (left) and between stabilizing selection gradients and competition coefficients (right) as a function of $2bV_{\\bar X}$ which is approximately equal to the ratio of variance in mean traits among species to the intraspecific trait variance. In both plots we set $c=1.0\\times10^{-4}$, $b=0.1$, $\\bar r=0.1$ and $N=1.0\\times10^{10}$ and let $V_{\\bar X}$ vary.'}
knitr::include_graphics('/home/bb/Gits/branching.brownian.motion.and.spde/cov.png')
```
We visualize these relationships in Figure \ref{cov_fig} for fixed $c,b,\bar r,U$ and $N$. In SM \S\ref{coef_grad_moms} we verify the qualitative nature of these relationships by repeating numerical integrations of system (\ref{comm_dynamics}) across a set of randomly drawn model parameters. We designed our numerical approach to inherit the assumptions of symmetric model parameters such as mutation rates $\mu_1=\dots=\mu_S$ and abiotic optima $\theta_1=\dots=\theta_S$ and to relax the key assumptions of normally distributed mean traits along with constant additive genetic variances and abundances across species.

@@

```{r, eval=F, echo=F}
require(ggplot2)
require(gridExtra)
df = read.csv("~/Research/Branching Brownian Motion/corrs.csv")
Cαβp = ggplot(df,aes(x=df$V/df$σ,y=df$Cαβ))+geom_point(size=0.1)+stat_smooth(color="black", method = "lm", formula = y ~ x + I(x^2) + I(x^3))+theme_minimal() + ylab("Correlation of \u03B1 and \u03B2")+xlab("Ratio of variance among \n species to variance within species")
Cαabsβp = ggplot(df,aes(x=df$V/df$σ,y=df$Cαabsβ))+geom_point(size=0.1)+stat_smooth(color="black", method = "lm", formula = y ~ x + I(x^2) + I(x^3))+theme_minimal()+ylab("Correlation of \u03B1 and |\u03B2|")+xlab("Ratio of variance among \n species to variance within species")
Cαγp = ggplot(df,aes(x=df$V/df$σ,y=df$Cαγ))+geom_point(size=0.1)+stat_smooth(color="black", method = "lm", formula = y ~ x + I(x^2) + I(x^3))+theme_minimal()+ylab("Correlation of \u03B1 and \u03B3")+xlab("Ratio of variance among \n species to variance within species")
Cαℭp = ggplot(df,aes(x=df$V/df$σ,y=df$Cαℭ))+geom_point(size=0.1)+stat_smooth(color="black", method = "lm", formula = y ~ x + I(x^2) + I(x^3))+theme_minimal()+ylab("Correlation of \u03B1 and ℭ")+xlab("Ratio of variance among \n species to variance within species")
corrsp = grid.arrange(Cαabsβp,Cαγp,nrow=1)
ggsave("/home/bb/Gits/branching.brownian.motion.and.spde/corrs.png",  corrsp,  width=6.5,height=2.5)
ggsave("/home/bb/Gits/branching.brownian.motion.and.spde/Cαℭp.png",   Cαℭp,  width=4,height=2.5)
```

```{r, echo=F, fig.align='center', out.width='60%', fig.cap='\\label{cor_coev_fig}Numerical estimates for the correlation of the strength of coevolution measured by $\\mathfrak{C}$ and competition coefficeints $\\alpha$ plotted against the variance of mean traits among species divided by the mean variance of traits within species. Each dot represents the result from a single simulation. The red line is a cubic regression.'}
knitr::include_graphics('/home/bb/Gits/branching.brownian.motion.and.spde/Cαℭp.png')
```

### 2020-04-28 Current-Version.tex
organize for overleaf

{\centering \includegraphics[width=1\linewidth]{/home/bb/Gits/branching.brownian.motion.and.spde/Current Version/cov}

@@

{\centering \includegraphics[width=0.6\linewidth]{/home/bb/Gits/branching.brownian.motion.and.spde/Current Version/Cαℭp}

>>>>

{\centering \includegraphics[width=1\linewidth]{/home/bb/Gits/branching.brownian.motion.and.spde/cov}

@@

{\centering \includegraphics[width=0.6\linewidth]{/home/bb/Gits/branching.brownian.motion.and.spde/Cαℭp}

### 2020-04-28 SM.Rmd
organize for overleaf

```{r, echo=F, fig.align='center', out.width='100%', fig.cap='\\label{num_corr} Numerical estimate for the correlations of selection gradients and competition coefficients.'}
knitr::include_graphics('/home/bb/Gits/branching.brownian.motion.and.spde/Current Version/corrs.png')
```

>>>>

```{r, echo=F, fig.align='center', out.width='100%', fig.cap='\\label{num_corr} Numerical estimate for the correlations of selection gradients and competition coefficients.'}
knitr::include_graphics('/home/bb/Gits/branching.brownian.motion.and.spde/corrs.png')
```
